INSTRUCTION SETS FOR STRANGERS

### 2022-02-06 f21/ms1/finalproject/7x7/7x7.tex
rectructureed things

\begin{document}
\maketitle
%\tableofcontents
%----------------------------------------------
\newpage
\subsection*{five (11/03/2021)}
\textbf{name:} trachea support trial no. 1

>>>>

\begin{document}
\maketitle
%\tableofcontents
%----------------------------------------------
\clearpage
\subsection*{five (11/03/2021)}
\textbf{name:} brainmelting openscad brachea exercise

\textbf{soundtrack:} Palomino by Trampled by Turtles then Norman Fucking Rockwell by Lana Del Rey

The intent of this prototype was to model a breachea in 3D for printing. I did a lot of thinking at work today and was not prepared to think more. Luckily, David, my brain multiplier was available. This is as far as I got.
\begin{figure}[h]
\centering
  \includegraphics[width=\textwidth]{images/53.png}
  \caption{the beginning of a 3d model}
\end{figure}

\clearpage
\subsection*{five (11/03/2021)}
\textbf{name:} trachea support trial no. 1

### 2022-02-06 f21/ms1/instructionsetsforstrangers/instructionsetsforstrangers.tex
rectructureed things

Combinging the feedback from class critique we needed to move forward on the three main areas of improvemnet:
\begin{itemize}
\item
  make the entire mechanism more robust for installation
\item
  make the hand and activation mechnaism more visible at night
\item
  change the activation mechnaism so that it is easier to understand how to activate the hand
\end{itemize}

@@

Next we found some $1/8$ inch and $3/4$ inch plywood and created the base of the new mechanishm. At this point we also determined the best way to make the handle to activate the hand waving easier to use. A handle that needs to be pulled is a bit ambiguous and not very visual, so we decided to make the handle another lever in the shape of a hand that would encourage users to use their hands to activate it. This was a simple lever that sticks out of one side of the mechanism pulled one side of the hand waving lever down when activated. \href{https://drive.google.com/file/d/1A4jMRefTUcI-PZPhbS6XSqFU6V4kzS8j/view?usp=sharing}{Link to video of lever action.}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth, angle=270]{"images/III/leverwithbase.jpg"}
\caption{Lever action.}
\end{figure}

@@

takeaways

no one wants to push hard on the hands

people who were more intoxicaed we re less gentle

>>>>

Combinging the feedback from class critique we needed to move forward on the three main areas of improvemnet:
\begin{itemize}
\item
  make the entire mechanism more robust for installation
\item
  make the hand and activation mechanism more visible at night
\item
  change the activation mechanism so that it is easier to understand how to activate the hand
\end{itemize}

@@

Next we found some $1/8$ inch and $3/4$ inch plywood and created the base of the new mechanism. At this point we also determined the best way to make the handle to activate the hand waving easier to use. A handle that needs to be pulled is a bit ambiguous and not very visual, so we decided to make the handle another lever in the shape of a hand that would encourage users to use their hands to activate it. This was a simple lever that sticks out of one side of the mechanism pulled one side of the hand waving lever down when activated. \href{https://drive.google.com/file/d/1A4jMRefTUcI-PZPhbS6XSqFU6V4kzS8j/view?usp=sharing}{Link to video of lever action.}  \href{https://drive.google.com/file/d/1zZMAdPojSRc_iC_QfIq4iEV6bjWMPP37/view?usp=sharing}{Link to video of the final lever mechanism.}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.6\textwidth]{"images/III/leverswithbase.png"}
\caption{Lever action.}
\end{figure}

Once the mechanism and base were dialed in, we painted the entire assembly using eye catching colors and a final layer of sparkly spray paint. The hope was that this would catch the light at night and make the hands more visible.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{"images/III/painting.JPG"}
\includegraphics[width=0.5\textwidth]{"images/III/elwire.JPG"}
\caption{Spray painted parts and installed EL wire.}
\end{figure}

We then added the electroluminescent wire around the perimeter of the large, waving hands and along the length of each lever to help attract more attention. Finally, after securing all the part in place, we were ready to install.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth]{"images/III/readytogo.JPG"}
\caption{Wave machine ready to install.}
\end{figure}

@@

Our installation too place in two parts. Once on the evening of September 17th and then again during later afternoon on September 26th. The first installation seems to generate more interest as it was later at night and the hands were more visible. During the second installation interest seems to increase as it became darker, however we were not able to stay and watch any later.

Once we arrived at the first installation site, around 9PM, our plans had to be modified slightly. There was a large construction pylon on one side of the intended intersection making the space to walk in the crosswalk quite narrow. We were concerned that adding the wave machine to this side of the intersection would interfere too much with accessibility to the crosswalk, so we chose the perpendicular crosswalk at the intersection instead. This was an unfortunate change as the perpendicular intersection had a large pile of bagged trash next to it which decreased the amount of space around the hand installed there. Nevertheless, there was considerable interest almost as soon as we put up the hands.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{"images/III/purplehandinstalled.JPG"}
\includegraphics[width=0.45\textwidth]{"images/III/greenhandinstalled.JPG"}
  \caption{Hands installed on adjacent street corners around 9 PM (notice trash below green hand).}
\end{figure}

We chose to mount them high enough that they wouldn't be run into very often, but low enough that they were still visible to people on the street. During the second installation we tried lowering the hands on the street pole. Many more people ran into the lever and, while they were more visible, it wasn't entirely clear if this made it easier or harder to use them.

Overall, the hands generated a lot of interest \href{https://drive.google.com/file/d/1pUGkjezofgZf2cuKnzpuoyqFLIYEEZ25/view?usp=sharing}{(see video of some "best of" interactions)}. The most challenging aspect of the installation process was waiting around long enough to observe good interactions. We would like to try installing the hands over a longer period of time and using a webcam to record all interactions.

One thing that surprised us was how delicate people on the street treated the levers of the machine. Many people -- particularly during the second installation -- would come up to the hands and push lightly on the levers, not quite making them wave. For subsequent installations we plan to tune the mechanism so that it requires less force to achieve an exciting result.

In conclusion, our interaction was quite effective! During the second installation we actually had a group of people wave at each other from across the street -- our intended result. By fine tuning the hands themselves, as well as our observation techniques, I think we can achieve more success in future installations.
